\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}

\begin{center}
    \textbf{\Huge Prakhar Verma} \\
    \vspace{0.2cm}
    Fort Wayne, IN | +1 (952) 219-1256 | \href{mailto:connect@iprakharv.com}{connect@iprakharv.com} | \href{https://www.linkedin.com/in/iprakharv}{LinkedIn} | \href{https://www.github.com/iPrakharV}{GitHub} \\
\end{center}

\section*{Education}
\textbf{Purdue University} \hfill \textit{May 2027} \\
Dean's \& Semester Honor's List | Honors College \hfill Indiana \\
\textbf{B.S. in Computer Science, Minor in Mathematics} \hfill \textbf{4.0 GPA} \\
Relevant Coursework: Data Structures and Algorithms, Object-Oriented Java Programming, Discrete Mathematics, Computer Architecture, Linear Algebra, Analytic Geometry, Calculus. \\

\textbf{The National Society of Leadership and Success (NSLS)} \hfill \textit{December 2023 - Present} \\
Nominated Member \hfill Fort Wayne, IN \\
Selected by Purdue for membership based on excellent academic standing and leadership potential. \\

\section*{Experience}
\textbf{Google Developer Group} \hfill \textit{July 2024 - Present} \\
Campus Organizer \hfill Fort Wayne, IN \\
\begin{itemize}[leftmargin=*]
    \item Organized Google technology-focused events, planning 25+ technical workshops annually to increase active participation.
    \item Collaborated with Google developers on sessions for Android, AI, web APIs, and cloud services.
    \item Launched a mentorship program linking 10,000+ students with industry pros for skill development.
\end{itemize}

\textbf{Medical Informatics Engineering, Inc.} \hfill \textit{May 2024 - Present} \\
Software Development Intern \hfill Fort Wayne, IN \\
\begin{itemize}[leftmargin=*]
    \item Developed AES-encrypted IoT access control system using Raspberry Pi 5 and ESP32, integrated with Apple Wallet for secure user authentication.
    \item Created a real-time voice transcription system using ASR technologies like Google's Speech Recognition, Mozilla's DeepSpeech, and OpenAI's WhisperAI, improving transcription accuracy and efficiency.
\end{itemize}

\textbf{Purdue FW Robotics Club} \hfill \textit{October 2023 - Present} \\
Vice-President \hfill Fort Wayne, IN \\
\begin{itemize}[leftmargin=*]
    \item Led the club in developing and implementing robotics projects using Arduino and OpenCV, enhancing practical engineering skills among members.
\end{itemize}

\textbf{CodeDay} \hfill \textit{April 2023 - Present} \\
Regional Manager \hfill Seattle, WA \\
\begin{itemize}[leftmargin=*]
    \item Led multiple hackathons across India, drawing 5000+ high school students across events.
    \item Hosted 50+ workshops on Python, Git, and transformer AI models, enhancing skills for 300+ attendees.
\end{itemize}

\section*{Projects}
\textbf{SafeFall} | OpenCV, MediaPipe, PyTorch, JavaScript, HTML5, CSS, Vercel, Raspberry Pi \hfill \textit{May 2024} \\
People’s Choice Winner- Regeneron \\
\begin{itemize}[leftmargin=*]
    \item Created SafeFall with OpenCV, aiming to enhance fall detection accuracy by 30\%.
    \item Utilized MediaPipe and PyTorch for real-time pose analysis, reducing false positives by 25\%.
\end{itemize}

\textbf{SkyCanvas} | Flask, Python, HTML, JavaScript, OpenCV \hfill \textit{April 2024} \\
\begin{itemize}[leftmargin=*]
    \item Developed software that processes drone positioning data in real-time, achieving 95\% accuracy.
    \item Implemented a Flask-based control platform, boosting user interaction efficiency by 30\%.
\end{itemize}

\section*{Honors \& Awards}
\begin{itemize}[leftmargin=*]
    \item Letter of Commendation, Defense Minister of India - top 3\% academic performance nationally.
    \item 1st Place Robotex India - RoboSumo, 1st Place Robo War - Robotex India, 1st place TechFest Zonal 2020.
\end{itemize}

\section*{Skills}
Languages: Java, Python, C++, Dart, Blueprint, Swift, HTML5, JavaScript, CSS3, Bhai-Lang, LaTeX, Bash \\
Tools \& Frameworks: Arduino, Raspberry Pi, ESP32, Firebase, Flutter, PyTorch, OpenCV, Flask, Git, IoT, Automation \\
Operating Systems: Linux, Ubuntu, macOS, Windows, Raspbian \\

\end{document}